\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-07-11 cubble.Rmd
minor chananges with arxiv submission

```{r illu-interactive, echo = FALSE, purl= FALSE, fig.align="center", out.height = "35%", out.width = "100%", fig.cap = "Linking between multiple plots is made possible by shared \\code{crosstalk} objects. When a station is selected on the map (a), the corresponding row in the spatial \\code{cubble} will be activated. This will activate the row with the same id in the temporal \\code{cubble} (b) to trigger an update of the line plot (c). The cubble package makes linking between spatial and temporal plots easy."}
knitr::include_graphics(here::here("figures/diagram-keynotes/‎diagram-keynotes.‎002.png")) 
```

>>>>

```{r illu-interactive, echo = FALSE, purl= FALSE, fig.align="center", out.height = "35%", out.width = "100%", fig.cap = "Linking between multiple plots is made possible by shared \\code{crosstalk} objects. When a station is selected on the map (a), the corresponding row in the spatial \\code{cubble} will be activated. This will activate the row with the same id in the temporal \\code{cubble} (b) to trigger an update of the line plot (c). The cubble package makes linking between spatial and temporal plots easy."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.002.png")) 
```

### 2023-07-11 cubble.tex
minor chananges with arxiv submission

{\centering \includegraphics[width=1\linewidth,height=0.35\textheight]{figures/diagram-keynotes/‎diagram-keynotes.‎002}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/cookd/students_PhD/Sherry/paper-cubble/figures/glyphmap-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/cookd/students_PhD/Sherry/paper-cubble/figures/matching-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/cookd/students_PhD/Sherry/paper-cubble/figures/netcdf-1}

>>>>

{\centering \includegraphics[width=1\linewidth,height=0.35\textheight]{figures/diagram-keynotes/diagram-keynotes.002}

@@

{\centering \includegraphics[width=1\linewidth]{figures/glyphmap-1}

@@

{\centering \includegraphics[width=1\linewidth]{figures/matching-1}

@@

{\centering \includegraphics[width=1\linewidth]{figures/netcdf-1}
